Causal Analysis Paper

### 2022-06-07 PaperAnalysis.Rmd

In the sensitivity analysis we would check which part of the total effect can be explained by the abortion laws and which can be explained by female literacy. Additionally, we check how much the effects would need to change to cancel one another.For instance, the effect for flexibility score alone I can check when I control (block) the primary completion rate.

>>>>

In the sensitivity analysis we would check which part of the total effect can be explained by the abortion laws and which can be explained by female literacy. Additionally, we check how much the effects would need to change to cancel one another.For instance, the effect for flexibility score alone I can check when I control (block) the primary completion rate.
Sensitivity analysis has 2 essential parts to it:
1)describing the type of unobserved confounders
Unmeasured variables: religious institutions, contraceptive prevalence, fertility rate 
2) plausibility that problematic confounding might exist
	Based on research design, 
expert knowledge and 
data-generating process
Generally, sensitivity analysis is still underutilized in social science and policy research papers (Sudan paper p. 40). However, it is a very useful tool to test robustness of findings, i.e. how sensitive my effects and effect sizes are to other variables that influence the treatment or outcome studied. Therefore, we are proposing to add a sensitivity analysis to the research design and also apply it in the second part of our report. This method gives us two insights: 1) the robustness value: how robust the coefficient is to confounders influencing treatment and outcome and 2) the proportion of the outcome uniquely explained by the treatment and how strong a confounder would have to be to eliminate the effect of the treatment. (Sudan paper pp.40/41)
